Say ``Hello World!''.

### 2025-05-15 Manuscript/Manuscript.tex
Added Repo Link

@@

% ABSTRACT
\begin{abstract}
	\langName{} is a programming language that looks like natural language. Leveraging React with Vue and Microsoft's ts-parsec library, the goal of this project was to show that a programming language can be made to look like English. Not only that, but on a fundamental level, the interpreter for \langName{} relies on semantic composition in order to derive the meaning of its sentences. While this type of language is largely inefficient, there are benefits in accessibility and interesting tie-ins with the field of semantics.
\end{abstract}

>>>>

% LINK STYLING
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

@@

% ABSTRACT
\begin{abstract}
	\langName{}\footnote{Link to Repository: \url{https://github.com/ProphecyOak/Vizzini/tree/v1.0.0}} is a programming language that looks like natural language. Leveraging React with Vue and Microsoft's ts-parsec library, the goal of this project was to show that a programming language can be made to look like English. Not only that, but on a fundamental level, the interpreter for \langName{} relies on semantic composition in order to derive the meaning of its sentences. While this type of language is largely inefficient, there are benefits in accessibility and interesting tie-ins with the field of semantics.
\end{abstract}
